Cloud Supercomputing

### 2019-03-07 writing/paper/paper.tex
Paper: Further copy/pasting, fix biblatex.

\documentclass[runningheads]{llncs}
\title{Clouds}
\author{$\ldots$}
\institute{$\ldots$}

@@

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
\section{Introduction}
\newcommand{\diffCoeff}{\varepsilon}
\newcommand{\hyperFluxDef}{
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure) \\
    \Qj \QZZ
  \end{pmatrix}
}
\newcommand{\viscFluxDef}{
  \begin{pmatrix}
    0\\
     \stressT (\Q, \gradQ)  \\
     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}\\
     0\\
   \end{pmatrix}
}%
We solve the reactive compressible Navier-Stokes equations in the conservative form% \pcref{eq:conservation-law-gradient}
\begin{equation}
 \label{eq:equation-set} 
%  \begin{array}{l}
%  \text{mass cons.} \\
%  \text{momentum cons.} \\
%  \text{energy cons.} \\
%  \text{cont.\ gas} 
% \end{array}
% :
\quad
  \pdv{}{t}
  \underbrace{
  \begin{pmatrix}
    \Qrho\\
    \Qj\\
    \QE\\
    \QZ
    \end{pmatrix}}_{\Q}
  +
  \divergence{
  \underbrace{
  \left(
   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
+
\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
  \right)}_{\flux(\Q, \gradQ)}}
 =
  \underbrace{
  \begin{pmatrix}
    \source[\Qrho\phantom{\Qrho}]\\
    \source[\Qj]\\
    \source[\QE]\\
    \source[\QZ]
    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
\end{equation}
which describes the time evolution of variables $\Q$ with respect to a flux $\flux(\Q, \gradQ)$ and a source $\source(\Q)$.
The vector of conserved quantities is given by
\begin{equation}
  \label{eq:conserved-variables}
 \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
\end{equation}
where $\Qrho$ is the density, $\Qj$ is the two or three-dimensional momentum, $\QE$ is the energy density and $\QZ$ is the mass fraction of the chemical reactant.
The pressure $\pressure$ is given by the equation of state of an ideal reacting gas
\begin{equation}
  \label{eq:eos}
  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right)  - q_0 \QZ - gz \right).
\end{equation}
The term $q_0 \QZ$ is the chemical energy with a heat release $q_0$~\cite{helzel2000modified}, the term $gz$ is the geopotential height with the gravity of Earth $g$~\cite{giraldo2008study}.
We model the diffusive effects of the flow by the standard stress tensor
\begin{equation}
  \label{eq:stress-tensor}
  \stressT(Q, \nabla Q) =
  \mu
  \left(
  \left(\nicefrac{2}{3} \divergence{\Qv} \right) -
  \left( \gradient{\Qv} + \gradient{\Qv}^\intercal \right)
  \right),
\end{equation}
with viscosity $\mu$.

Many realistic, atmospheric flows can be described by a pertubation over a background state that is in hydrostatic equilibrium
\newcommand{\backgroundPressure}{\overline{\pressure}}
\newcommand{\backgroundRho}{\overline{\Qrho}}
\begin{equation}
  \label{eq:hydrostatic-balance}
  \pdv{}{z} \backgroundPressure{\left (z \right )} = -g \backgroundRho(z).
\end{equation}
The momentum equation is dominated by the background flow in this case.
This leads to numerical instabilities.
We avoid this by splitting the pressure $\pressure = \backgroundPressure + \pressure'$ and density $\Qrho = \backgroundRho + \Qrho'$
\begin{equation}
  \label{eq:momentum-equation-split}
  \pdv{\Qj}{t}+ \divergence{ \left(
    \Qv \otimes \Qj + \bm{I} \pressure'
    \right)
  } + \viscFlux_\Qj
  =
  -g \bm{k} \Qrho'.
\end{equation}

@@

\section{Methods}
Maybe numerics (dg+muscl?), at least ref.
Exahype?!

@@

Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.
The total variation (\textsc{tv}) of this function is defined by
\begin{equation}
  \label{eq:tv}
  \tv \left[ f(\bm{x}) \right] =
  \Vert
\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert }
\Vert_1
\end{equation}
for each cell.
The operator $\Vert \cdot \Vert_1$ denotes the discrete $l_1$ norm in this equation.
We compute this efficiently with Gaussian quadrature over the collocated quadrature points.
\newcommand{\mean}{\mu}%
\newcommand{\std}{\sigma}%
\newcommand{\variance}{\std^2}%
\newcommand{\Trefine}{T_\text{refine}}%
\newcommand{\Tdelete}{T_\text{delete}}%
How can we decide whether a cell is important or not?
To resolve this conundrum, we compute the mean and the population standard deviation of the total variation of all cells.
It is important to note that we use the method of Chan/LeVeque to compute the modes in a parallel and numerical stable manner.
A cell is then considered to contain significant information if its deviates from the mean more than a given threshold.
This criterion can be described formally by
\begin{equation}
  \label{eq:refinement-criterion}
  \operatorname{evaluate-refinement}(\Q, \mu, \sigma) =
  \begin{cases}
    \text{refine} & \text{if } \tv(\Q) \geq \mu + \Trefine \sigma \\
    \text{delete} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma \\
    \text{keep} & \text{otherwise}.
    \end{cases}
\end{equation}
The parameters $\Trefine > \Tdelete$ can be chosen freely.
Chebyshev's inequality
\begin{equation}
  \label{eq:chebychev}
  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2},
\end{equation}
with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells.
This inequality holds for arbitrary distributions under the weak assumption that they have a mean $\mu$ and standard deviation $\sigma$~\cite{wasserman2004all}.

@@

A simple scenario is the Taylor-Green vortex.
It has an analytical solution in the incompressible limit
The solution is
\begin{align}
  \label{eq:taylor-green}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1,\\
  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
  \begin{pmatrix}
    \phantom{-}\sin(x) \cos(y) \\
- \cos(x) \sin(y) 
    \end{pmatrix}, \\
  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \nicefrac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C,
  \end{split}
\end{align}
where $C = \nicefrac{100}{\gamma}$ is a constant that governs the speed of sound and thus the Mach number~\cite{dumbser2016high}.
We use a viscosity of $\mu = 0.1$ and Cauchy boundary conditions.

We use the Arnold–Beltrami–Childress (\textsc{abc}) flow as a simple three-dimensional flow~\cite{tavelli2016staggered}.
It also has an exact solution under the assumption of incompressibility
\begin{align}
  \label{eq:abc-flow}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1,\\
  \Qv(\bm{x}, t) &= \phantom{-} \exp(-1\mu t)
  \begin{pmatrix}
    \sin(z) + \cos(y)\\
    \sin(x) + \cos(z)\\
    \sin(y) + \cos(x)
  \end{pmatrix}, \\
  \pressure(\bm{x}, t) &= -\exp(-2 \mu t) \, \left(\cos(x)\sin(y) + \sin(x)\cos(z) + \sin(z)\cos(y)\right)
  + C
  \end{split}
\end{align}
Here, $C = \nicefrac{100}{\gamma}$ is an arbitrary constant.
We use a viscosity of $\mu = 0.01$ and Cauchy boundary conditions.

As a final example of standard flow scenarios, we consider the lid-driven cavity flow which initial conditions are given by a fluid at rest, with $\pressure = \text{?}$, etc.
We consider a domain of size $1 \times 1 \text{?}$ which is surrounded by no-slip walls.
The flow is driven entirely by the upper wall which has a velocity of $v_x = 1$.

Clouds with 2+ AMR Levels (if working?)

Reactive Detonation Waves (maybe with stiff source term and/or fixed bcs)

\section{Conclusion}
\end{document}

>>>>

\documentclass[runningheads]{llncs}
\title{Cloud Supercomputing}
\author{$\ldots$}
\institute{$\ldots$}
\usepackage[american]{babel}
\usepackage[autostyle, english = american]{csquotes}
\usepackage[%
  % backend=biber,
  % url=false,
  % style=alphabetic,
  % backref=true,
  % hyperref=true,
  % maxnames=4,
  % minnames=3,
  % maxbibnames=99,
  % firstinits,
  % uniquename=init
  ]{biblatex}
\DefineBibliographyStrings{english}{%
  backrefpage = {see p.},
  backrefpages = {see pp.}
}
\addbibresource{../bibliography.bib}

@@

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
\section{Introduction}
\newcommand{\diffCoeff}{\varepsilon}
\newcommand{\hyperFluxDef}{
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure) \\
    \Qj \QZZ
  \end{pmatrix}
}
\newcommand{\viscFluxDef}{
  \begin{pmatrix}
    0\\
     \stressT (\Q, \gradQ)  \\
     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}\\
     0\\
   \end{pmatrix}
}%
We solve the reactive compressible Navier-Stokes equations in the conservative form% \pcref{eq:conservation-law-gradient}
\begin{equation}
 \label{eq:equation-set} 
%  \begin{array}{l}
%  \text{mass cons.} \\
%  \text{momentum cons.} \\
%  \text{energy cons.} \\
%  \text{cont.\ gas} 
% \end{array}
% :
\quad
  \pdv{}{t}
  \underbrace{
  \begin{pmatrix}
    \Qrho\\
    \Qj\\
    \QE\\
    \QZ
    \end{pmatrix}}_{\Q}
  +
  \divergence{
  \underbrace{
  \left(
   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
+
\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
  \right)}_{\flux(\Q, \gradQ)}}
 =
  \underbrace{
  \begin{pmatrix}
    \source[\Qrho\phantom{\Qrho}]\\
    \source[\Qj]\\
    \source[\QE]\\
    \source[\QZ]
    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
\end{equation}
which describes the time evolution of variables $\Q$ with respect to a flux $\flux(\Q, \gradQ)$ and a source $\source(\Q)$.
The vector of conserved quantities is given by
\begin{equation}
  \label{eq:conserved-variables}
 \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
\end{equation}
where $\Qrho$ is the density, $\Qj$ is the two or three-dimensional momentum, $\QE$ is the energy density and $\QZ$ is the mass fraction of the chemical reactant.
The pressure $\pressure$ is given by the equation of state of an ideal reacting gas
\begin{equation}
  \label{eq:eos}
  \pressure = (\gamma - 1) \left(\QE - \frac{1}{2} \left(\Qv \cdot \Qj \right)  - q_0 \QZ - gz \right).
\end{equation}
The term $q_0 \QZ$ is the chemical energy with a heat release $q_0$~\cite{helzel2000modified}, the term $gz$ is the geopotential height with the gravity of Earth $g$~\cite{giraldo2008study}.
We set $\QZZ$ and $q_0$ to zero for scenarios without a reactive component.
We model the diffusive effects of the flow by the standard stress tensor
\begin{equation}
  \label{eq:stress-tensor}
  \stressT(Q, \nabla Q) =
  \mu
  \left(
  \left(\nicefrac{2}{3} \divergence{\Qv} \right) -
  \left( \gradient{\Qv} + \gradient{\Qv}^\intercal \right)
  \right),
\end{equation}
with viscosity $\mu$.

Many realistic, atmospheric flows can be described by a pertubation over a background state that is in hydrostatic equilibrium
\newcommand{\backgroundPressure}{\overline{\pressure}}
\newcommand{\backgroundRho}{\overline{\Qrho}}
\begin{equation}
  \label{eq:hydrostatic-balance}
  \pdv{}{z} \backgroundPressure{\left (z \right )} = -g \backgroundRho(z).
\end{equation}
The momentum equation is dominated by the background flow in this case.
This leads to numerical instabilities.
We avoid this by splitting the pressure $\pressure = \backgroundPressure + \pressure'$ and density $\Qrho = \backgroundRho + \Qrho'$
\begin{equation}
  \label{eq:momentum-equation-split}
  \pdv{\Qj}{t}+ \divergence{ \left(
    \Qv \otimes \Qj + \bm{I} \pressure'
    \right)
  } + \viscFlux_\Qj
  =
  -g \bm{k} \Qrho'.
\end{equation}
The right side of this equation is implemented as a source term.

\todo{Notation? Introduce $T$}For reactive problems, we use the simple reaction model
\begin{equation}
  \label{eq:reaction-model}
  \source[\QZ] = - \frac{1}{\reactionTimescale} \left[T > \reactionTemperature \right]\QZ
\end{equation}
where $\reactionTimescale$ is the time scale of the reaction and $\reactionTemperature$ is the critical temperature~\cite{hidalgo2011ader,helzel2000modified}.
We only consider the case of $\reactionTimescale \geq 10^{-2}$ which corresponds to a non-stiff source.

@@

\section{Methods}
\todo{Write \aderdg{}/\exahype{} section!}
Maybe numerics (dg+muscl?), at least ref.
Exahype?!

@@

Let $\bm{f}(\bm{x}): \mathbb{R}^{N_\text{vars}} \to \mathbb{R}$ be a function that maps the discrete solution at a point $\bm{x}$ to an arbitrary indicator variable.
The total variation (\textsc{tv}) of this function is defined by
\begin{equation}
  \label{eq:tv}
  \tv \left[ f(\bm{x}) \right] =
  \Vert
\intdcell{ \vert \gradient{f \left( \bm{x} \right)} \vert }
\Vert_1
\end{equation}
for each cell.
The operator $\Vert \cdot \Vert_1$ denotes the discrete $l_1$ norm in this equation.
We compute this efficiently with Gaussian quadrature over the collocated quadrature points.
\newcommand{\mean}{\mu}%
\newcommand{\std}{\sigma}%
\newcommand{\variance}{\std^2}%
\newcommand{\Trefine}{T_\text{refine}}%
\newcommand{\Tdelete}{T_\text{delete}}%
How can we decide whether a cell is important or not?
To resolve this conundrum, we compute the mean and the population standard deviation of the total variation of all cells.
It is important to note that we use the method of Chan/LeVeque to compute the modes in a parallel and numerical stable manner.
A cell is then considered to contain significant information if its deviates from the mean more than a given threshold.
This criterion can be described formally by
\begin{equation}
  \label{eq:refinement-criterion}
  \operatorname{evaluate-refinement}(\Q, \mu, \sigma) =
  \begin{cases}
    \text{refine} & \text{if } \tv(\Q) \geq \mu + \Trefine \sigma \\
    \text{delete} & \text{if } \tv(\Q) < \mu + \Tdelete \sigma \\
    \text{keep} & \text{otherwise}.
    \end{cases}
\end{equation}
The parameters $\Trefine > \Tdelete$ can be chosen freely.
Chebyshev's inequality
\begin{equation}
  \label{eq:chebychev}
  \mathbb{P}(\vert X - \mu \vert \geq c \sigma) \leq \frac{1}{c^2},
\end{equation}
with probability $\mathbb{P}$ guarantees that we neither refine nor delete all cells.
This inequality holds for arbitrary distributions under the weak assumption that their mean $\mu$ and standard deviation $\sigma$ are finite~\cite{wasserman2004all}.

@@

\todo{Constants of fluids?}
A simple scenario is the Taylor-Green vortex.
It has an analytical solution in the incompressible limit which is given by
\begin{align}
  \label{eq:taylor-green}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1,\\
  \Qv(\bm{x}, t) &= \exp(-2 \mu t)
  \begin{pmatrix}
    \phantom{-}\sin(x) \cos(y) \\
- \cos(x) \sin(y) 
    \end{pmatrix}, \\
  \pressure(\bm{x}, t) &= \exp(-4 \mu t) \, \nicefrac{1}{4} \left( \cos(2x) + \cos(2y) \right) + C.
  \end{split}
\end{align}
In this equation, $C = \nicefrac{100}{\gamma}$ is a constant that governs the speed of sound and thus the Mach number~\cite{dumbser2016high}.
We use a viscosity of $\mu = 0.1$ and Cauchy boundary conditions.

We use the Arnold-Beltrami-Childress (\textsc{abc}) flow as a simple three-dimensional flow~\cite{tavelli2016staggered}.
It also has an exact solution under the assumption of incompressibility
\begin{align}
  \label{eq:abc-flow}
  \begin{split}
  \Qrho(\bm{x}, t) &= 1,\\
  \Qv(\bm{x}, t) &= \phantom{-} \exp(-1\mu t)
  \begin{pmatrix}
    \sin(z) + \cos(y)\\
    \sin(x) + \cos(z)\\
    \sin(y) + \cos(x)
  \end{pmatrix}, \\
  \pressure(\bm{x}, t) &= -\exp(-2 \mu t) \, \left(\cos(x)\sin(y) + \sin(x)\cos(z) + \sin(z)\cos(y)\right)
  + C
  \end{split}
\end{align}
Here, $C = \nicefrac{100}{\gamma}$ is an arbitrary constant.
We use a viscosity of $\mu = 0.01$ and Cauchy boundary conditions.

As a final example of standard flow scenarios, we consider the lid-driven cavity flow which initial conditions are given by a fluid at rest, with $\Qrho = 0, \pressure(\bm{x}) = \nicefrac{100}{\gamma}$.

We consider a domain of size $\SI{\pi}{m} \times \SI{\pi}{\m} \text{?}$ which is surrounded by no-slip walls.
The flow is driven entirely by the upper wall which has a velocity of $v_x = \SI{1}{\m/s}$.
\begin{equation}\label{eq:atmosphere-constants}
    \gamma = 1.4 ,\qquad \Pr =  0.71 ,\qquad R = 287.058 ,\qquad p_0 = 10000, \qquad g = 9.81,
\end{equation}
Our atmospheric flow scenarios are described in terms of the potential energy
\begin{equation}
  \potT = T \left( \frac{p_0}{p} \right)^{R/c_p},
\end{equation}
with the reference pressure $p_o = \SI{10e5}{\Pa}$.

We compute the initial background density and pressure by inserting the assumption of a constant background energy in \cref{eq:hydrostatic-balance}.
The background atmosphere is then perturbed.
\todo{What about our weird boundary condition for heat flux and energy?}
Let
\begin{equation}
  \label{eq:radius}
  r^2 = (x - x_0)^2 + (z - z_0)^2
\end{equation}
denote the difference between spatial positions $x,z$ and the center of a bubble $x_c, z_c$.
For our first scenario, the cosine bubble, we use a pertubation of the form
\begin{equation}
  \label{eq:cos-pertubation-alt}
  \pertubationPotT = 
    \nicefrac{A}{2} \left( 1 + \cos(\pi r) \right) \left[ r \leq a \right]
\end{equation}
\begin{align}
  \label{eq:cos-pertubation}
  \pertubationPotT &= \begin{cases}
    \nicefrac{A}{2} \left[ 1 + \cos(\pi r) \right] & r \leq a, \\
    0 & r > a,
    \end{cases}
\end{align}
where $A$ denotes the maximal perturbation and $a$ is the size of the bubble.
We use the constants
\begin{equation}\label{eq:cosine-bubble}
  A = 0.5 \quad a = \SI{250}{\m} \quad x_c = \SI{500}{\m} \quad z_c = \SI{350}{\m}.
\end{equation}
We use a constant viscosity of $\mu = 0.1$.
For our second scenario, the cold bubble on top of a warm bubble, we use the pertubation of the form
\begin{equation}
  \label{eq:bubbles-pertubation}
  \pertubationPotT =
  \begin{cases}
    A & r \leq a, \\
    A \exp \left( - \frac{(r-a)^2}{s^2} \right) & r > a,
    \end{cases}
\end{equation}
where $s$ is the decay rate and $r$  is the radius to the center~\pcref{eq:radius}.
We have two bubbles, with constants
\begin{equation}
  \label{eq:bubbles-values}
\begin{alignedat}{6}
  & \text{warm:} \qquad && A = 0.5, \quad&& a = \SI{150}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{500}{\m,} \quad&& z_c = \SI{300}{\m},\\
  & \text{cold:} \qquad && A = -0.15, \quad&& a = \SI{0}{\m}, \quad&& s = \SI{50}{\m}, \quad&& x_c = \SI{560}{\m}, \quad&& z_c = \SI{640}{\m}.
  \end{alignedat}
\end{equation}
Similar to~\cite{muller2010adaptive} and to the previous scenario, we use a constant viscosity of $\mu = 0.1$ to regularize the solution.

We start with a coarse mesh that is then subdivided up to two times in an adaptive manner.
For this we use the criterion of \cref{eq:refinement-criterion} with parameters xxx and xxx.
We compare this with a simulation obtained by a fully refined grid.

Clouds with 2+ AMR Levels (if working?)
Reactive Detonation Waves (maybe with stiff source term and/or fixed bcs)
Finally, we consider the radialsymmetric detonation wave of xxx, which uses the coupled advection-reaction equation.
Its initial conditions are given by xxx.
We evaluate this scenario both with a viscosity xxx and with zero viscosity.

\section{Conclusion}
Insert conclusion here.

\printbibliography{}
\end{document}
